---
title: "Week 6 Day 2 Homework"
output:
  html_document:
    toc: yes
    toc_float: true
    toc_depth: '2'
    highlight: tango
    df_print: paged
---

# MVP

## Question 1

```{r}
library(tidyverse)
library(janitor)
library(skimr)

phones <- read_csv("data/20190928-items.csv")

phones <- clean_names(phones)

skim(phones)
```

The ratings appear to be on a 1-5 scale, the mean and median are similar.

The total reviews have very different mean and medians, I believe this means the data is skewed. It appears to be right skewed as mean > median and by comparing the values of p75 and p100 it looks like there are outliers  towards the high numbers. 




## Question 2

```{r}
phones %>% 
  group_by(brand) %>% 
  summarise(num_phones = n()) %>% 
  slice_max(num_phones)
```
Samsung has the highest number of phones at 397. 


## Question 3

```{r}
phones_stats <- phones %>% 
  filter(brand == "Samsung") %>% 
  summarise(
    num = n(),
    mean = mean(rating), 
    sd = sd(rating)
  )


phones %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating)) + 
  geom_histogram(aes(y = after_stat(density)),
                 col = "white", 
                 binwidth = 0.1) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = phones_stats$mean, 
      sd = phones_stats$sd
    ),
    col = "red"
  )
```

The normal distribution appears to fit the data quite well, although there are some clear outliers at the high and low ends of the x scale. 

## Question 4

sd = 0.6847859

```{r}
# ok to use nrow(phones) here as there are no missing ratings in the dataset

within_1_sd <- phones %>% 
  filter(between(rating, 
                 phones_stats$mean - phones_stats$sd, 
                 phones_stats$mean + phones_stats$sd)) %>% 
  summarise(n() / nrow(phones)) %>% 
  pull()

within_2_sd <- phones %>% 
  filter(between(rating, 
                 phones_stats$mean - (2*phones_stats$sd), 
                 phones_stats$mean + (2*phones_stats$sd))
         ) %>% 
  summarise(n() / nrow(phones)) %>% 
  pull()


within_3_sd <- phones %>% 
  filter(between(rating, 
                 phones_stats$mean - (3*phones_stats$sd), 
                 phones_stats$mean + (3*phones_stats$sd))
         ) %>% 
  summarise(n() / nrow(phones)) %>% 
  pull()

normal_distr <- c(0.68, 0.95, 0.997)
Q4_distr <- c(within_1_sd, within_2_sd, within_3_sd)
how_many_sd <- c("within_1_sd", "within_2_sd", "within_3_sd")

comparison <-  tibble(how_many_sd,
                      "normal_distrbution" = normal_distr, 
                      "Q4_distribution" = Q4_distr)

comparison
```


```{r}
comparison %>% 
  pivot_longer(cols = 2:3, names_to = "distribution", values_to = "proportion_of_ratings") %>% 
  ggplot(aes(x = how_many_sd, y = proportion_of_ratings)) +
  geom_col(aes(fill = distribution), position = "dodge")
```

The proportion of ratings found within 1 SD of the mean is 78%. This is higher than for a normal distribution where this figure is 68%. This suggests the distribution is narrower in shape and has a smaller standard deviation. 
A normal distribution has SD of 1 and our data has SD of 0.68 so this makes sense.
The proportion of ratings found within 2 and 3 SDs of the mean are quite similar to a normal distribution. 

```{r}
phones %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating)) + 
  geom_histogram(aes(y = after_stat(density)),
                 col = "white", 
                 binwidth = 0.1) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = phones_stats$mean, 
      sd = phones_stats$sd
    ),
    col = "red"
  ) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = phones_stats$mean, 
      sd = 1
    ),
    col = "blue"
  ) 
```

# 2 Extension

```{r}
library(ggpubr)
```

```{r}
ggdensity(phones$rating)
```

```{r}
ggqqplot(phones$rating)
```

```{r}
shapiro.test(phones$rating)
```

Hmmm the website says p-value > 0.05 means distribution of data is not significantly different from normal distribution. 
Our data gives a tiny p-value which suggests the data is very different from a normal distribution. This is in contrary to what I deduced above in question 4. 

## Alternative way using qqnorm
```{r}
qqnorm(phones$rating)
```
The line is straight in the middle but curves off at the end which can mean the data has more extreme values than would be expected in a nor mal distribution. 

