---
title: "Week 11 Day 5 Homework - Logistic Regression"
output:
  html_document:
    toc: yes
    toc_float: true
    toc_depth: '2'
    highlight: tango
    df_print: paged
---

```{r}
library(tidyverse)
library(janitor)
library(glmulti)
library(caret)
library(modelr)
library(pROC)
library(GGally)
```

```{r}
juice <- read_csv("data/orange_juice.csv") %>% 
  clean_names()
```

```{r}
juice_clean <- juice %>% 
  mutate(purchase_mm = ifelse(purchase == "MM", "yes", "no"), .before = purchase) %>% 
  # special_mm and special_ch removed as every observation is "yes"
  select(-purchase, -special_ch, -special_mm)


```

**What to do about weekly data**

```{r}
ggplot(juice_clean, aes(weekof_purchase, fill = purchase_mm)) +
  geom_bar()

```

The data covers a year but there is reallly no obvious pattern of which type of OJ is bought throughout the year. 
There may be some differences in proportions for different quarters so lets convert the data to quarters. 

```{r}
juice_clean <- juice_clean %>% 
  mutate(quarter_of_purchase = case_when(
    weekof_purchase < 240 ~ "Q1",
    weekof_purchase < 253 ~ "Q2",
    weekof_purchase < 266 ~ "Q3",
    TRUE ~ "Q4"
  ), .before = "store_id") %>% 
  select(-weekof_purchase)
```

Changing other variables to factors

```{r}
juice_clean <- juice_clean %>% 
  mutate(purchase_mm = as_factor(purchase_mm),
         quarter_of_purchase = as_factor(quarter_of_purchase),
         store_id = as_factor(store_id))

```


```{r}
alias(purchase_mm ~ ., data = juice_clean)
```

store is made from store_id and store7. I think I'll keep the store_id column. 
list_price_diff is made up from the two price columns so we dont' need it
price_diff is made up from 4 other columns, its complicated but I don't think we need it.
Lastly, sale_price_mm and sale_price_ch are made up from the price and disc columns. Do we want to keep the sale price or the discount, lets keep sale price. 

```{r}
juice_clean <- juice_clean %>% 
  select(-c(store, store7, list_price_diff, price_diff, disc_ch, disc_mm))
```

```{r}
alias(purchase_mm ~ ., data = juice_clean)
```

No more alias'


## Split Data

```{r}
train_index <- createDataPartition(juice_clean$purchase_mm,
                                   p = 0.8,
                                   list = FALSE, 
                                   times = 1)

train <- juice_clean[train_index, ]
test <- juice_clean[-train_index, ]


```


```{r, message = FALSE}
ggpairs(juice_clean, progress = FALSE)



```



## glmulti

```{r}
glmulti_search_all_mains <- glmulti(
  purchase_mm ~ ., 
  data = train,
  level = 1,               # No interactions considered, main effects only
  method = "h",            # Exhaustive approach
  crit = "bic",            # BIC as criteria
  confsetsize = 10,        # Keep 10 best models
  plotty = F, 
  report = T,              # No plots, but provide interim reports
  fitfunction = "glm",     # glm function
  family = binomial(link = "logit")) # binomial family for logistic regression

summary(glmulti_search_all_mains)
```

```{r}
glmulti_search_previous_mains_one_pair <- glmulti(
  purchase_mm ~ 1 + loyal_ch + sale_price_mm + sale_price_ch, 
  data = train,
  level = 2,               # Interactions considered
  method = "h",            # Exhaustive approach
  crit = "bic",            # BIC as criteria
  confsetsize = 10,        # Keep 10 best models
  marginality = TRUE,      # consider pairs only if both main effects in model
  minsize = 6,             # minsize, maxsize and marginality here force 
  maxsize = 6,             # inclusion of a single pair beyond the five main effects
  plotty = F, 
  report = T,              # No plots, but provide interim reports
  fitfunction = "glm",     # glm function
  family = binomial(link = "logit")) # binomial family for logistic regression

summary(glmulti_search_previous_mains_one_pair)

```

```{r}
glmulti_search_previous_mains_one_pair@objects[[1]]
```

```{r}
glmulti_interactions <- glm(purchase_mm ~ 1 + loyal_ch + sale_price_mm + sale_price_ch + sale_price_mm:loyal_ch + sale_price_ch:loyal_ch + sale_price_ch:sale_price_mm,
                            data = juice_clean, 
                            family = binomial(link = "logit"))


juice_clean_pred_interactions <- juice_clean %>% 
  add_predictions(glmulti_interactions, type = "response")

roc_with_interactions <- juice_clean_pred_interactions %>% 
  roc(response = purchase_mm, predictor = pred)


ggroc(data = roc_with_interactions)


threshold <-  0.5

juice_clean_pred_interactions_thresh <- juice_clean_pred_interactions %>% 
  mutate(pred_thresh_0.5 = pred >= threshold)
  
conf_table <- juice_clean_pred_interactions_thresh %>%
  tabyl(purchase_mm, pred_thresh_0.5)

conf_table
```


