---
title: "Week 2 Day 2 Homework"
output:
  html_document:
    toc: yes
    toc_float: true
    toc_depth: '2'
    highlight: tango
    df_print: paged
editor_options: 
  chunk_output_type: console
---

## Question 1

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.


```{r}
library(tidyverse)
library(CodeClanData)
```

```{r}
view(backpack)
glimpse(backpack)
skimr::skim(backpack)
summary(backpack)
```
The data has 100 rows and 9 columns. There are 6 numeric and 3 factor columns. There are no missing values. 

## Question 2

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
ggplot(backpack) +
  aes(backpack_weight) +
  geom_bar() +
  scale_y_continuous(breaks = 1:13)
```

The backpack weights range from 2 to 35. There are 12 backpacks which weigh 10, this is the highest number of any single weight. The mean weight is 11.66 and the median is 11. 

## Question 3

Are there differences in backpack weight between sex?

```{r}
backpack %>% 
  group_by(backpack_weight, sex) %>% 
  summarise(num_backpacks = n())%>% 
ggplot() +
  aes(backpack_weight, num_backpacks, colour = sex) +
  geom_line() 

ggplot(backpack) + 
  aes(backpack_weight, fill = sex) + 
  geom_bar(position = "dodge", width = 1) +
  facet_grid(~sex)

# need to half the sizes of the bars

```
The weight differences of backpacks between males and females is not obvious. You could maybe say that the weight of backpacks carried by males is spread over a wider range, while female backpack weight is more concentrated around 10. 

## Queston 4

What is the relationship between body weight and backpack weight?

```{r}
ggplot(backpack) +
  aes(backpack_weight, body_weight) +
  geom_point() +
  geom_smooth(method = "lm")
```
This data does not show a relationship between body weight and backpack weight. 

## Question 5

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
ggplot(backpack) +
  aes(backpack_weight, body_weight, colour = sex) +
  geom_point() +
  geom_smooth(method = "lm")
```

For males there is still no relationship between body weight and backpack weight. For females there is perhaps a slight relationship but it looks like it is still within the error range. 

## Question 6

What proportion of students report back pain?
```{r}
backpack %>% 
  mutate(back_problems = factor(back_problems)) %>% 
  group_by(back_problems) %>% 
  summarise(num_backpacks = n()) %>% 
ggplot() +
  aes(x = back_problems, y = num_backpacks) +
  geom_col()
```



## Question 7

Is this proportion different between men and women?

```{r}
backpack %>% 
  mutate(back_problems = factor(back_problems)) %>% 
ggplot() +
  aes(sex) +
  geom_bar(aes(fill = back_problems), position = "fill")
```
Yes, proportionally more woman than men have back problems. 

## Question 8

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.

```{r}
ggplot(backpack) +
  aes(backpack_weight, body_weight, colour = sex) +
  geom_point() +
  geom_smooth(method = "lm")
```



# Extension

## Question 1

Does reported backpain differ across the year groups? Ignore year 0 in your data.









## Question 2

Is there a difference between how heavy the bags those in different years carry?

