---
title: "Day 3 Homework"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
movies <- read_csv("movies.csv")
```

**Question 1**
Ideas for investigating data:
- Is there a way to find the rows where 'title' and 'original_title' are different?
- Column names are all in an acceptable format so no work needed there
- revenue and budget both relate to money but the numbers are formatted differently,
could convert so they match
- orignal language should be changed to be more clear (am assuming en = english)
- popularity would be better if it were on a clearer scale e.g. out of 100
- check dates in release dates are all the same format
- there's some NA and zero values in various columns which may need dealt with
before further analysis

**Question 2**

```{r}
# having a look at the movies which have different entries in the 'title' and 
# original_title columns

movies %>% 
  filter(title != original_title)

# a lot of the entires in original_title are in a language other than English
# as we are working in English lets use the 'title' variable going forward

```

```{r}
movies_selected <- movies %>% 
  select(title, runtime, budget)
movies_selected
```

**Question 3**

```{r}
# how many NA values are there in the movies_selected dataframe?
sum(is.na(movies_selected))
# there are 2, lets find which columns they are in 

movies_selected %>% 
  filter(is.na(title)) %>% 
  summarise(title_NAs = n()) 
# there are no NAs in the title column

movies_selected %>% 
  filter(is.na(runtime)) %>% 
  summarise(runtime_NAs = n())
# there are 2 NAs in runtime column

movies_selected %>% 
  filter(is.na(budget)) %>% 
  summarise(budget_NAs = n())
# as expected there are no NAs in budget

# this seems like a convoluted way of doing this, must be a quicker way?
```

**Question 4**

```{r}
movies_runtime <- movies_selected %>% 
  mutate(runtime = na_if(runtime, 0))

movies_runtime %>% 
  filter(is.na(runtime)) %>% 
  summarise(runtime_NAs = n())
```
Now there are 37 NAs in runtime

**Question 5**



```{r}
movies_imputed <- movies_runtime %>%
  mutate(runtime = coalesce(runtime, median(runtime, na.rm = TRUE)))
  
movies_imputed %>% 
  filter(is.na(runtime)) %>% 
  summarise(runtime_NAs = n())
```

**Question 6**

```{r}
movies_imputed %>% 
  arrange(runtime) %>% 
  head(10)
```

```{r}
movies_imputed %>% 
  arrange(desc(runtime)) %>% 
  head(10)
```

**Question 7**

```{r}
movies_imputed <- movies_imputed %>% 
  mutate(budget = if_else(budget < 100, median(budget), budget))
```

**EXTENSION**
**Question 1**

```{r}
movie_budgets <- movies_imputed %>% 
  mutate(budget_type = case_when(
    budget < 12000000 ~ "Small budget",
    budget < 40000000 ~ "Medium budget",
    TRUE ~ "Big budget"
  ))
```

**Question 2**



```{r}
movies %>% 
  summarise(sum(is.na(across(where(is.character)))))
```

```{r}
movies %>% 
  summarise(sum(is.na(across(where(is.numeric)))))
```

