---
title: "Week 10 Day 3 Homework"
output:
  html_document:
    toc: yes
    toc_float: true
    toc_depth: '2'
    highlight: tango
    df_print: paged
---

# MVP

## Question 1

```{r}
library(tidyverse)
library(GGally)
library(ggfortify)
library(fastDummies)
library(mosaic)
library(modelr)
```

```{r}
houses <- read_csv("data/kc_house_data.csv")
```

```{r}
summary(houses)
```

No missing data

```{r, tidying data for regression}
# removing columns that aren't needed
houses_tidy <- houses %>% 
  select(-c(date, id, sqft_living15, sqft_lot15, zipcode)) %>% 
# converting waterfront column to logical
  mutate(waterfront = as.logical(waterfront)) %>% 
# converting yr_renovated to logical renovated column
  mutate(yr_renovated = ifelse(yr_renovated == 0, FALSE, TRUE)) %>% 
  rename(renovated = yr_renovated) %>% 
# convert view to factor (categorical ordinal)
  mutate(view = factor(view, levels = c(0, 1, 2, 3, 4))) %>% 
# convert condition to factor (categorical ordinal)
  mutate(condition = factor(condition, levels = c(1, 2, 3, 4, 5))) %>% 
# lets group together grade - low (1-3), average (4-10), high (11-13)
  mutate(grade = case_when(
    grade < 4 ~ "low", 
    grade >10 ~ "high",
    TRUE ~ "average"
  ),
  grade = factor(grade, levels = c("low", "average", "high"))
  )
```

## Question 2

```{r}
alias(lm(price ~ ., data = houses_tidy))
```

alias has detected that sqft_basement can be calculated from sqft_living minus sqft_above. 
This means we can removed sqft_basement. 

```{r}
houses_tidy <- houses_tidy %>% 
  select(-sqft_basement)
```

## Question 3

```{r}
houses_tidy_numeric <- houses_tidy %>%
  select_if(is.numeric)

houses_tidy_nonnumeric <- houses_tidy %>%
  select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- houses_tidy$price
```

```{r, message = FALSE}
ggpairs(houses_tidy_numeric, progress = FALSE)
```


**Correlation with price - Numeric Variables**

Strong positive correlations
1. sqft_living (0.702)
2. sqft_above (0.606)

Moderate correlation
3. bathrooms (0.525)

Weak correlations
4. bedrooms (0.308)
5. latitude (0.307)
6. floors (0.257)

Very week correlations
7. sqft_lot (0.09)
8. yr_built (0.054)
9. longitude (0.022)



```{r, message = FALSE}
ggpairs(houses_tidy_nonnumeric, progress = FALSE)
```

**Correlation with price - Non-Numeric Variables**

waterfront - appears to affect price

View - there is a correlation with price, the median of the 5 levels generally increases with better views (less obvious between levels 1 and 2). The highest and lowest levels of view clearly have an effect on price.

condition - no obvious correlation here

grade - looks like a good correlation here with a decent increase in price related to the highest grade of building. This looks like the strongest correlation from the non-numeric variables. 

renovated - may be a correlation but not a strong one from looking at boxplots

Conclusion 
predictors to investigate in order of potential
grade = "high"
waterfront = TRUE
view = 4 (or view - 0, I'm not sure)

### First Predictor - sqft_living

```{r}
model1 <- lm(price ~ sqft_living,
             data = houses_tidy)

summary(model1)
```

```{r}
autoplot(model1)
```

```{r}
plot(model1)
```


Not sure these diagnostic plots look great but have plotted the data below and I think the issue is caused by the shape of the data. It appears to have very defined cut-offs but I don't know why?


```{r}
houses %>% 
  ggplot(aes(price, sqft_living)) +
  geom_point(alpha = 0.1)
```

Conclusion
I have reservations about the shape of the data and consquently the diagnostic plots but lets go with this for now. 
R2 = 0.493
rse = 261500 (this is really quite high!)
p-value < 0.01


### Second Predictor

The next strongest correlation for the numeric variables was sqft_above but this is really very similar to sqft_living so lets not do it next. Bedrooms has a moderate correlation with price so try that next. 

```{r}
model2 <- lm(price ~ sqft_living + bedrooms, 
             data = houses_tidy)

summary(model2)
```
R2 = 0.507 so not added much from model 1 (R2 = 0.493)
rse = 257800 still very high 

```{r}
autoplot(model2)
```
```{r}
plot(model2)

houses %>% 
  slice(15871)
```



We seem to be fiting a negative values - what is going on here?

```{r}
houses %>% 
  ggplot(aes(price, bedrooms)) + 
  geom_point()
```

So there is a house with over 30 bedrooms. This was investigated. This house is noted as having 33 bedrooms but costing $640000. All the other houses that cost this much (there were 21) had between 2 and 6 bedrooms, this is therefore assumed to be a typo and the number of bedrooms changed to 3. 

```{r}
houses_tidy <- houses_tidy %>% 
  mutate(bedrooms = ifelse(bedrooms > 30, 3, bedrooms)) 
```

Run model and diagnostic again...

```{r}
model2b <- lm(price ~ sqft_living + bedrooms, 
              data = houses_tidy)

summary(model2b)
```

The R2 and rse are similar to model2 but the diagnostics should look better. 

```{r}
autoplot(model2b)
```

Hmmm, for plot 2 the residuals are getting larger as the prices get higher. 
For scale-location, the blue line is not flat and I think it should be. Am starting to have my doubts about using sqft_livng, there is something not right with this data. 

Does sqft_above look any better?

```{r}
houses_tidy %>% 
  ggplot(aes(price, sqft_above)) +
  geom_point()
```

No the sqft_above data looks the same as sqft_living

What if we just try bedrooms on its own as the first predictor?

### First predictor (again!)

```{r}
model1b <- lm(price ~ bedrooms, 
              data = houses_tidy)

summary(model1b)
```

R2 is low, bedrooms isn't explaining much of the variation. I think we have to go with sqft_living. 

Lets press on with model2b (price ~ sqft_living + bedrooms(with 33 altered))

### Third Predictor

```{r}
model3 <- lm(price ~ sqft_living + bedrooms + waterfront, 
             data = houses_tidy)

summary(model3)
```

We're up to R2 = 0.542 now, rse reducing slightly but still very high. 
p-values very low and diagnostic plots ok

```{r}
autoplot(model3)
```

We're up to R2 = 0.542 now, rse reducing slightly but still very high. 
p-values very low and diagnostic plots ok (ish) (I think??)
Something odd has happened to leverage graph

## Fourth Predictor

Lets look at the residuals to see what can best explain them. 

```{r}
houses_resid <- houses_tidy %>% 
  add_residuals(model3)
```

```{r}
houses_tidy_numeric <- houses_resid %>%
  select_if(is.numeric)

houses_tidy_nonnumeric <- houses_resid %>%
  select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$resid <- houses_resid$resid
```





```{r, message = FALSE}
ggpairs(houses_tidy_numeric, progress = FALSE)
```

**Correlation with Residuals - Numeric Columns**

latitude - weak positive (0.396) close to being moderate though
yr_built - weak negative (-0.240)


```{r, message = FALSE}
ggpairs(houses_tidy_nonnumeric, progress = FALSE)
```


**Correlation with Residuals - Non-Numeric Columns**

grade = "high" is showing a bit of correlation 
None of the others are very convincing

Add grade as 4th predictor

```{r}
model4 <- lm(price ~ sqft_living + bedrooms + waterfront + grade,
             data = houses_tidy)

summary(model4)
```

R2 is now 0.57 with rse 240800
grade = "high" has a p-value < 0.01 but grade = "average" has a high p-value and is not significant.

```{r}
autoplot(model4)
```

```{r}
plot(model4)
```

```{r}
anova(model3, model4)
```

Adding grade is statistically significant

```{r}
anova(model2b, model3)
```

Adding waterfront is statistically significant. 