---
title: "Week 6 Day 1 Homework"
output:
  html_document:
    toc: yes
    toc_float: true
    toc_depth: '2'
    highlight: tango
    df_print: paged
---

#1.1 The Titanic

```{r}
library(tidyverse)
library(gtools)
```


# 1.2 Probability Consolidation Questions

## Question 1

```{r}
die <- c(1, 2, 3, 4, 5, 6)

less_than_five <- c(1,2,3,4)


q1_prob <- length(less_than_five) / length(die)
q1_prob

```
The probability of rolling a number less than five is 2/3 or 0.6667. 

## Question 2

```{r}
q2_num_outcomes <- permutations(6, 3, die, repeats.allowed = TRUE)

nrow(q2_num_outcomes)
```



## Question 3

```{r}
q3_num_outcomes <- as_tibble(permutations(n = 6, r = 4, v = die, repeats.allowed = TRUE))

q3_num_outcomes <- q3_num_outcomes %>% 
                    mutate(total = rowSums(.)) 

q3_total_5_to_7 <- q3_num_outcomes %>% 
  filter(between(total, 5, 7))

q3_prob <- nrow(q3_total_5_to_7) / nrow(q3_num_outcomes)
q3_prob

```

There are 34 outcomes where the total of the 4 dice equals 5, 6 or 7.

The probability of getting a total of 5, 6 or 7 is 0.02623

The die rolls are independent.

## Question 4

```{r}
heights <- c(1, 2, 3, 4, 5)


q4_num_outcomes <- permutations(n = 5, r = 5, v = heights, repeats.allowed = FALSE)
q4_num_outcomes

# Only one permutation is right

q4_prob <- 1 / nrow(q4_num_outcomes)
q4_prob
```

The probability of people sitting in order of height (decreasing left to right) is 0.008333. There is only one permutation that satisfies this so we divide 1 by the total number of permutations, which is 120.

## Question 5

```{r}
q5_num_outcomes <- permutations(n = 6, r = 6, v = die, repeats.allowed = TRUE)

q5_prob_1 <- 1 / nrow(q5_num_outcomes)
q5_prob_1
```

There is only one combination which can be 6, 5, 4, 3, 2, 1 so to work out the probability of this occuring we divide 1 by total number of permutations. The probability is 2.14e-05

```{r}
q5_num_outcomes_no_repeats <- permutations(n = 6, r = 6, v = die, 
                                           repeats.allowed = FALSE)
q5_num_outcomes_no_repeats

q5_prob_2 <- nrow(q5_num_outcomes_no_repeats) / nrow(q5_num_outcomes)
q5_prob_2
```

The probability of throwing one of each of the numbers is 0.0154.

## Question 6

0.5
